\chapter*{Overview of Part~\ref{part:data_integration}}

In Part~\ref{part:data_integration}, we focus on building tools and frameworks to enable data integration and semantic enrichment of enterprise data. We highlight the various challenges and tackle them in an incremental manner.

In Chapter~\ref{chapter:part2-background}, we overview the background of our work in Data Integration and semantic enrichment. We first introduce basic concepts in Business Intelligence and various relevant tools in the SAP ecosystem. We finally overview relevant social media outlets that can expose relevant information useful for the decision making process.

In Chapter~\ref{chapter:rubix}, we identify the need for an enterprise knowledge base. We detail the challenges and design decisions to import DBpedia into SAP HANA. We further present a set of tools that enable entity disambiguation, entity properties rankings and semantic enrichment on top of DBpedia. We also enhance an in-house schema matching tool called AMC with a set of matchers that show that using Linked Data to map cell values with instances and column headers with types improves significantly the quality of the matching results and therefore should lead to more informed business decisions.

In Chapter~\ref{chapter:snarc}, we note that aggregating relevant social news is not an easy task. We present a semantic social news aggregation framework called SNARC. SNARC is a service that uses semantic web technology and combines services available on the web to aggregate social news. SNARC brings live and archived information to the user that is directly related to his active page. The key advantage is an instantaneous access to complementary information without the need to dig for it. Information appears when it is relevant enabling the user to focus on what is really important.