\chapter*{List of Publications}

\section*{Journal}\label{sec:journals}

\begin{enumerate}
 \item \underline{\textbf{Ahmad Assaf}}, {R}apha{\"e}l {T}roncy and {A}line {S}enart: \textbf{Towards An Objective Assessment Framework for Linked Data Quality}. International Journal On Semantic Web and Information Systems, \emph{under review}, 2015.
\end{enumerate}

\section*{Conferences}\label{sec:conferences}

\begin{enumerate}
\item \underline{\textbf{Ahmad Assaf}}, {R}apha{\"e}l {T}roncy and {A}line {S}enart: \textbf{{A}utomatic Validation, Correction and Generation of Dataset Metadata - {E}nhancing Dataset Search and Spam Detection}. In 24th {I}nternational {W}orld {W}ide {W}eb {C}onference (WWW 2015), Demo Track, May 2015, {F}lorence, {I}taly.
\item \underline{\textbf{Ahmad Assaf}}, {G}hislain {A}temezing, {R}apha{\"e}l {T}roncy and {E}lena {C}abrio: \textbf{{W}hat are the important properties of an entity? {C}omparing users and knowledge graph point of view}. In 11th {E}xtended {S}emantic {W}eb {C}onference (ESWC 2014), Demo Track, May 2014, {H}eraklion, {C}rete.
\item \underline{\textbf{Ahmad Assaf}}, {A}line {S}enart and {R}apha{\"e}l {T}roncy: \textbf{{SNARC} - An Approach for Aggregating and Recommending Contextualized Social Content}. In 10th {E}xtended {S}emantic {W}eb {C}onference (ESWC 2013), Sattelite Events, May 2013, {M}ontpellier, {F}rance. \textbf{1$^{st}$ Prize Winner of the AI Mashup Challenge}
\end{enumerate}

\section*{Workshops}\label{sec:workshops}

\begin{enumerate}
\item \underline{\textbf{Ahmad Assaf}}, {R}apha{\"e}l {T}roncy and {A}line {S}enart: \textbf{{W}hat's up {LOD} Cloud - Observing The State of Linked Open Data Cloud Metadata}. In 2$^{nd}$ Workshop on Linked Data Quality (LDQ), May 2015, {P}ortoroz, {S}lovenia.
\item \underline{\textbf{Ahmad Assaf}}, {R}apha{\"e}l {T}roncy and {A}line {S}enart: \textbf{{HDL} - Towards A Harmonized Dataset Model for Open Data Portals}. In 2$^{nd}$ {I}nternational {W}orkshop on {D}ataset {PROFI}ling \& f{E}derated {S}earch for {L}inked {D}ata (PROFILES), May 2015, {P}ortoroz, {S}lovenia.
\item \underline{\textbf{Ahmad Assaf}}, {R}apha{\"e}l {T}roncy and {A}line {S}enart: \textbf{{A}n Extensible Framework to Validate and Build Dataset Profiles}. In 2$^{nd}$ {I}nternational {W}orkshop on {D}ataset {PROFI}ling \& f{E}derated {S}earch for {L}inked {D}ata (PROFILES), May 2015, {P}ortoroz, {S}lovenia. \textbf{Best paper award}
\item \underline{\textbf{Ahmad Assaf}}, {A}line {S}enart and {R}apha{\"e}l {T}roncy: \textbf{{D}ata Quality Principles in the Semantic Web}. In International Workshop on Data Quality Management and Semantic Technologies (DQMST), July 2012, {P}alermo, {I}taly.
\item \underline{\textbf{Ahmad Assaf}}, {E}ldad {L}ouw, {A}line {S}enart, {C}orentin {F}ollenfant {R}apha{\"e}l {T}roncy and {D}avid {T}rastour: \textbf{{RUBIX}: a Framework for Improving Data Integration with Linked Data}. In 1$^{st}$ International Workshop on Open Data (WOD), June 2012, {N}antes, {F}rance.
\end{enumerate} 